\section{Classification Task}
\label{sec:classification}
In this section I will describe the classification task that I have implemented, the way the dataset has been preprocessed and the results obtained with the different models.

\subsection{Data Preprocessing}
\label{sec:preprocessing}

\subsubsection{Feature selection}
\label{sec:preprocessing-feature-selection}
The first step is to select the features that will be used for the classification task.
The dataset for each drone contains the following 7 features: the position, the velocity and the target position of the drone and the angle between the drone and the target (relative to the north).
Since the angle is redundant since it can be computed from the position and the velocity (or also from the position and the target position), I have decided to remove it from the dataset.
The dataset is then composed by $6 \times 5 = 30$ features for the 5 drones in the environment and the label, which is the number of collisions.

\subsubsection{Normalization}
\label{sec:preprocessing-normalization}
Since the dataset contains features with different ranges, it is necessary to normalize the dataset.
Since each row represents an environment, the normalization is performed for each row separately.
The dataset also have data with different semantic meaning, so it is not possible to use a global normalization.
In fact the position of the drone is an absolute value (refer to the point (0,0) in space), while the velocity is a relative value (it's the difference between the current position and the previous one) it's not good to use the same normalization for both of them.
So this is the approach that I have decided to use:
\begin{itemize}
    \item \textbf{Positions}: since position and target position have an absolute meaning, I have used the min-max normalization for each row with the following formula:
    \begin{equation}
            \norm(x_{D^i}) = \frac{x_{D^i} - minCoord}{maxCoord - minCoord}
            \qquad \qquad
            \norm(y_{D^i}) = \frac{y_{D^i} - minCoord}{maxCoord - minCoord}
    \end{equation}
    Where:
    \begin{conditions}
        maxX & $\max\limits_{1 \leq i \leq 5} x_{D^i}$\\

        maxY & $\max\limits_{1 \leq i \leq 5} y_{D^i}$\\
    
        minX & $\min\limits_{1 \leq i \leq 5} x_{D^i}$\\

        minY & $\min\limits_{1 \leq i \leq 5} y_{D^i}$\\

        maxCoord & $\max(maxX, maxY)$\\

        minCoord & $\min(minX, minY)$
    \end{conditions}
    In this way, after normalization, the position of the drones (and their target positions) will be in the range [0, 1].
    The sample now represents a new "environment" where the bottom-left corner corresponds at the position of the drone (or the target position) with the smallest x and y coordinates and it will also preserve the aspect ratio of the original one.
    The chose about preserving the aspect ratio is because it showed better results in the experiments.
    
    \item \textbf{Velocity}: since it has a relative meaning, have been used the predefined $maxCoord$ and $minCoord$ values to normalize the data with the following formula:
    \begin{equation}
            \norm(vx_{D^i}) = \frac{x_{D^i}}{maxCoord - minCoord}
            \qquad \qquad
            \norm(vy_{D^i}) = \frac{y_{D^i}}{maxCoord - minCoord}
    \end{equation}
\end{itemize}

\subsubsection{Splitting}
\label{sec:preprocessing-splitting}
The dataset has been splitted in training and test set with a ratio of 80/20 in a stratified way, so that the distribution of the classes is the same in the training and test set.

\subsubsection{Balancing}
\label{sec:preprocessing-balancing}
The dataset is unbalanced, so it is necessary to balance it.
I have tried different methods for oversampling but since there are $<3$ samples of the minority class after splitting, the standard oversampling (such as SMOTE or Random Over Sampling) methods are not really effective.
Therefore, I have decided to implement my own oversampling method.

The idea is to use the semantic meaning of the dataset to generate new samples.
The environment is a 2D plane with drones having a position, a velocity and a target.
So I have decided to generate new samples by changing the position of the drones, keeping the velocity and the angle between the drone and the target constant.
In fact it is possible to move the drones backwards (using the inverse of velocity) and in this way new samples having the same number of collisions can be generated.

Since the distribution of the classes is not uniform (e.g. the probability of having 4 collisons is lower than the probability of having 3 collisions or 2 collisions, etc.), I have decided to generate same number of samples for each class.

\subsection{Training}
\label{sec:training}

\subsubsection{Classification models}
\label{sec:training-classifier-selection}
I have compared different classifiers for this task.
\begin{itemize}
    \item \textbf{Logistic Regression}
    \item \textbf{Random Forest}
    \item \textbf{Support Vector Machine}
    \item \textbf{Gaussian Naive Bayes}
\end{itemize}



\subsubsection{Hyperparameter tuning}
\label{sec:training-hyperparameter-tuning}
I have used the GridSearchCV method to tune the hyperparameters of the classifiers.
The hyperparameters that I have tuned are:
\begin{itemize}
    \item \textbf{Logistic Regression}: C
    \item \textbf{Random Forest}: n\_estimators, max\_depth
    \item \textbf{Support Vector Machine}: C, gamma
    \item \textbf{Gaussian Naive Bayes}: var\_smoothing
\end{itemize}
The best hyperparameters for each classifier are reported in Table [...].

\subsection{Evaluation}
\label{sec:evaluation}
[...]
